---
title: "Untitled"
author: "Nathan Craig"
date: "2/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(geojsonio)
library(ggplot2)
library(httr)
library(leaflet)
library(sf)
```

# Read GeoJSON with `geojsonio`

This library converts the file into an `sp`.

```{r}
spdf <- geojson_read(here::here("data/query.json"),  what = "sp")
```



[sp Gallery](https://edzer.github.io/sp/) and a useful SO [answer](https://stackoverflow.com/a/50213419/13110995) when importing and plotting.

```{r}
# plot(spdf)
```

## Leaflet plot using SP
```{r}
leaflet(data = spdf) %>% 
  addPolylines()
```

## Leaflet plot with additional styling
Note this is the same as doing it with `sf`. However, I figured it out first with `sf`.
```{r}
# Color pallet
pal <- colorFactor(palette = "Set1",
                   domain = spdf$Project_Status)

# Popup column
spdf$label <-  paste0(spdf$Project_Name1,"<br>",
                         "Length: ", spdf$Project_Length, "<br>",
                         "<a href=\"",spdf$`Image`,"\">","Photo","</a>")

# Plot
leaflet(data = spdf) %>% 
  addPolylines(color = ~pal(Project_Status),
               popup = spdf$label)
```



# Convert SP to SF and trying again

## Conversion
```{r}
sfdf <- st_as_sf(spdf)
```


## Leaflet plot using SF

Once I got this working, I did find and replate to direct the code to the `sp` data frame. It seems to work fine.

```{r}
# Color pallet
pal_wall <- colorFactor(palette = "Dark2",
                   domain = sfdf$Project_Status)

# Popup column
sfdf$label <-  paste0(sfdf$Project_Name1,"<br>",
                         "Length: ", sfdf$Project_Length, "<br>",
                         "<a href=\"",sfdf$`Image`,"\">","Photo","</a>")
# Plot
leaflet(data = sfdf) %>% 
  addPolylines(color = ~pal_wall(Project_Status),
               popup = sfdf$label) %>% 
  addLegend("bottomright", pal = pal_wall, values = ~Project_Status)
```

